Exploring Homicide Trends in Toronto: A Seventeen-Year Statistical Overview (2004-2020)

### 2024-01-19 outputs/paper/paper.qmd
More small fixes

The structure of the paper is as follows: the data section details the data processing techniques employed in the study, afterwards is a brief discussion of the data set, followed by insight into the variables of interest. The analysis begins with the Yearly Homicide Trends section and is devoted to presenting and discussing the key findings, including yearly homicide numbers and trends, the geographical distribution of these incidents, and the analysis of the prevalent methods of homicide. The concluding section synthesizes these insights, drawing out their implications for urban policy, community safety strategies, and the broader societal understanding of urban violence in Toronto. This study not only sheds light on the current state of urban homicides in Toronto but also sets the stage for future research and policy development in this critical area.

# Data

@@

# The Dataset:

@@

# Variables of Interest:

@@

# Yearly Homicide Trends
Our analysis delves into the details of homicide trends in the Greater Toronto Area (GTA) from 2004 to 2020, revealing insights about the nature and distribution of these violent incidents.

@@

# Geographical Distribution of Homicides

@@

# Predominance of Shooting as a Homicide Method

@@

# Conclusion

@@

Code and data supporting this analysis is available at:\
https://github.com/AlexanderG123/toronto_homicide

>>>>

The structure of the paper is as follows: Section 2 details the data processing techniques employed in the study, afterwards is a brief discussion of the data set, followed by insight into the variables of interest. Section 3 is devoted to presenting and discussing the key findings, including yearly homicide numbers and trends, the geographical distribution of these incidents, and the analysis of the prevalent methods of homicide. The concluding section synthesizes these insights, drawing out their implications for urban policy, community safety strategies, and the broader societal understanding of urban violence in Toronto. This study not only sheds light on the current state of urban homicides in Toronto but also sets the stage for future research and policy development in this critical area.

Code and data supporting this analysis is available.[^1]

[^1]: https://github.com/AlexanderG123/toronto_homicide

# Section 2: Data

@@

# 2.1 The Dataset:

@@

# 2.2 Variables of Interest:

@@

# Section 3: Analysis and Data Visualization

Our analysis delves into the details of homicide trends in the Greater Toronto Area (GTA) from 2004 to 2020, revealing insights about the nature and distribution of these violent incidents.

# 3.1 Yearly Homicide Trends

@@

# 3.2 Geographical Distribution of Homicides

@@

# 3.3 Predominance of Shooting as a Homicide Method

@@

# Section 4: Conclusion

@@
